Modelling the travel time of transit vehicles in \rt through a GTFS-based road network using GPS vehicle locations

### 2019-08-03 anzjs2018/sections/04_implementation.tex
altering graphs

The application consists of two components:
the first handles importing static GTFS data and constructing the network,
while the second implements the \rt models and prediction.
We used Rcpp \citep{Rcpp}
to develop the program,
which provides access to other R packages for data manipulation 
as well as the speed and memory management capabilities of C++.
The program is implemented in the R package
\verb+transitr+, available on Github (\url{https://github.com/tmelliott/transitr}).
In this section, we discuss the features of the \rt component
and assess its performance 
both with respect to timing and parameter estimation.

>>>>

The application consists of two components:
the first handles importing static GTFS data and constructing the network,
while the second implements the \rt models and prediction.
We used Rcpp \citep{Rcpp}
to develop the program,
which provides access to R \citep{rcore},
which contains many useful tools for data manipulation and package development,
as well as the speed and memory management capabilities of C++.
The program is implemented in the R package
\verb+transitr+, available on Github (\url{https://github.com/tmelliott/transitr}).
In this section, we discuss the features of the \rt component
and assess its performance 
both with respect to timing and parameter estimation.
